Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-08 README.Rmd
updated readme

@@

- Figure out discrepancies with old and new versions of the training data
- Rerun the lime explanations with the finalized training data
- Write up dataset descriptions in README and convert to a txt document for the submission
- Write up steps for creating the submission folder
- Update all files in the submission folder
- Consider getting rid of CyBox folder
- Delete old repo with long version
- Upload the files for submission, finish filling in questions, and submit!

@@

- `code-file-organization.R` contains R code for organizing the files to be added to the GitHub repository and generating a file with code for submission.
- `code-paper.R` contains the R code extracted from `paper.Rnw` using code in `code-file-organization.R`.
- `data-bullet-test.csv.zip` and `data-bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `data-example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
- `figure-readme.png` is a figure used in the readme.
- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- `README.Rmd` and `README.md` are the readme files that generated this output. :)
- `references.bib` contains the bibtex information for the 
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.

@@

**Need to write...**

@@

1. Knit paper (to make sure everything is up to date).
2. Run the code in the file code-extract-paper-code.R to produce an R script with all of the code from the manuscript (paper.Rnw).
3. **Need to finish...**

>>>>

- Figure out discrepancies with old and new versions of the training data
- Rerun the lime explanations with the finalized training data
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Update all files in the submission folder
- Finish filling in questions in ASA submission document
- Upload the files for submission and submit

@@

@@

- `code-file-organization.R` contains R code for organizing the files to be added to the GitHub repository and generating a file with code for submission.
- `code-paper.R` contains the R code extracted from `paper.Rnw` using code in `code-file-organization.R`.
- `code-trim-sig-data.R` contains R code for preparing the data in the file `data-example-signatures.csv.zip` based on data provided by Heike (that are not included in this directory).
- `data-bullet-test.csv.zip` and `data-bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `data-example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
- `figure-readme.png` is a figure used in the readme.
- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- `README.Rmd` and `README.md` are the readme files that generated this output. :)
- `references.bib` contains the bibtex information for the 
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.

@@

The data used in the manuscript for the bullet comparison examples is described below.

`data-bullet-train`: Contains comparison features from the Hamby 173 and 252 sets.

`data-bullet-test`: Contains comparison features from the Hamby 224 Clone sets. As with all Hamby sets, Hamby set 224, is a collection of 35 bullets, organized as 20 known bullets and 15 questioned bullets. The known bullets are fired in pairs of two through one of ten consecutively manufactures P-85 barrels. Clone set 224 is arranged as a test set of fifteen tests, one for each questioned bullet. Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. The test asks for a decision on whether the questioned bullet comes from the same source as the two known bullets or from a different source. This situation is similar to what a firearms and toolmarks examiner might encounter in case work.

`data-example-signatures`: Contains the signature data from two bullet-lands that are a match. The variables in the data are as follows:

  - land = Indicates where the observation corresponds to 'Signature 1' or 'Signature 2'
  - x = The x position of the signature
  - sig = The y position of the signature

@@

1. Knit the file `paper.Rnw` (to make sure everything is up to date).
2. Run the code in the file `code-file-organization.R` for producing an R script with all of the code from the manuscript (paper.Rnw).
3. Move the following files to the `submission` folder:
    - `code-paper.R`
    - `data-bullet-test.csv`
    - `data-bullet-train.csv`
    - `data-example-signatures.csv`
    - `figure/figure-XX-1.eps` (for XX = 01-07, 09, 11-13, B1, B2, and C3)
    - `figure-08-1.eps`
    - `figure-10-1.eps`
    - `paper.tex`
    - `readme.txt`
    - `references.bib`
    - `WileyNJD-AMS.bst`
    - `WileyNJD-v1.csl`
4. Change the name of `paper.tex` to `paper-submission.tex`.
5. Delete `figure/` from the figure file paths in `paper-submission.tex`. For example, change \includegraphics[width=6.5in]{figure/figure-01-1} to \includegraphics[width=6.5in]{figure-01-1}.
6. Compile the file `paper-submission.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly. 
7. Besides for `paper-submission.pdf`, delete all other files generated when `paper-sumbission.tex` was compiled. This includes other `paper-submission` files and pdf versions of the figures.
8. Convert the following files in the submission folder to a zip file, call it `code-and-data.zip`, and then delete the unzipped versions of the files:
    - `code-paper.R`
    - `data-bullet-test.csv`
    - `data-bullet-train.csv`
    - `data-example-signatures.csv`
    - `readme.txt`
9. Upload all remaining files to ASA data science journal submission page (except for `paper-submission.Rnw`) which should be:
    - `code-and-data.zip`
    - `figure-01-1.eps` through `figure-C3-1.eps`
    - `paper-sumbission.pdf`
    - `paper-sumbission.tex`
    - `references.bib`
    - `WileyNJD-AMS.bst`
    - `WileyNJD-v2.cls`
